### 2021-01-09 README.Rmd
renamed plot_posterior_parameters() and changed its sp behavior

# Plot posteriors
plot_ex <- posterior_param_ex %>%
  plot_posterior_parameters()
plot_ex[["lambda"]]
```

@@

```{r}
# Fit model with cross-validation
ex_bw <- focal_vs_comp_ex %>%
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

>>>>

# Plot posteriors
plot_ex <- posterior_param_ex %>%
  plot_bayesian_model_parameters()
plot_ex[["lambda"]]
```

@@

```{r}
# Fit model with cross-validation
ex_bw <- focal_vs_comp_ex %>%
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid_sf) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))
